Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-16 papers/ms.tex
update ms for auto Cep-Her groups

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching the full set of candidate Cep-Her
members against known Kepler Objects of Interest
\citep{thompson_planetary_2018} yielded four candidate cluster
members: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.  Given our
previous analysis of Kepler-1627, we will mostly focus on the latter
three.  After analyzing the relevant properties of Cep-Her
(Section~\ref{sec:cluster}), we discuss the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of implications for the size-evolution of close-in
mini-Neptunes (Section~\ref{sec:disc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points (see Section~\ref{subsec:members}).
  Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster
  \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\} \approx
  \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$ pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  longitudinal tangential velocity versus galactic latitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.
  There is a strong spatial and kinematic overlap between Kepler-1643
  and RSG-5 ($\{ l, b\} \approx \{ 82^\circ,
  6^\circ\}$; $\{ X, Y, Z\} \approx \{60, 330, 50\} $ pc).  The
  local population of candidate young stars around KOI-7368 and
  KOI-7913 is more diffuse -- we call this region ``CH-2'',
  and treat it with additional skepticism
  The {\bf interactive figure} enables overplotting the candidate
  cluster members.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy roughly 200 to 500 parsecs from
the Sun, above the galactic plane, and spanning galactic longitudes of
roughly $40^\circ$ to $100^\circ$ degrees.  Two of the richest
clusters in this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Both of these clusters were known before Gaia, and have reported ages
between $\approx$30 and $\approx$60 million years.  Early
empirical evidence that these two clusters might be part of a broader
population was apparent in the Gaia-based photometric analysis of
pre-main-sequence stars by \citet[][see their Figures~11 and~13]{Zari2018}.
Further kinematic connections and complexity were highlighted by
\citet{KounkelCovey2019}, when defining the structures they dubbed
``Theia~73'' and ``Theia~96''\footnote{A useful visualization is
available online at \url{http://mkounkel.com/mw3d/mw2d.html} (accessed
15 March 2022)}.  This connection by \citet{KounkelCovey2019} was made
as part of an unsupervised clustering analysis of the Gaia DR2
positions and tangential velocities with a subsequent manual
``stitching'' step, and generally supports the idea that there is an
overdensity of $30$--$60\,{\rm Myr}$ old stars in this region of the
Galaxy.  \citet{Kerr2021}, in a volume-limited analysis of the Gaia
DR2 point-source catalog out to one third of a kiloparsec, identified
three of the nearest sub-populations, dubbed ``Cepheus-Cygnus'',
``Lyra'', and ``Cerberus''.  \citet{Kerr2021} reported ages for each
of these subgroups between 30 and 35 million years.

@@

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and a few nearby
sub-populations in this quadrant of the sky share a common origin has
yet to be fully substantiated.  To further explore the population of
$10$--$100\,{\rm Myr}$ stars in this region, we select candidate
members through four steps, the first three being identical to those
described in Section~3 of \citet{Kerr2021}.  We briefly summarize them
here.

The first step is to select stars that are photometrically distinct
from the field star population based on Gaia EDR3 magnitudes $\{G,
G_{\rm RP}, G_{\rm BP}\}$, parallaxes and auxiliary reddening
estimates \citep{lallement_gaia-2mass_2019}.  This step yielded \npms\
stars, which are either  pre-main-sequence K and M dwarfs due to their
long contraction timescales, or massive stars near the zero-age main
sequence due to their rapid evolutionary timescales.

The second step is to then perform in an unsupervised HDBScan
clustering on the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The specific
parameters we use in this clustering analysis are $\{ X, Y, Z, c v_b,
c v_{l^*} \} $, where $c$ is the size-velocity corrective factor,
which is taken as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the
spatial and velocity scales have identical standard deviations.
Positions are computed assuming the \texttt{astropy v4.0} coordinate
standard \citep{astropy_2018}, which places the Sun $8122$ pc from the
galactic center, and assumes the solar velocity with respect to the
local standard of rest from \citet{schonrich_local_2010}.  As input
parameters to HDBScan, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$ parsecs in physical space,
and $c$ \kms\ in velocity.  The minimum cluster size $N$ is set to 10,
as is $k$, the parameter used to define the ``core distance'' density
metric.

This unsupervised clustering in our case yielded 8 distinct groups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects that are spatially and
kinematically consistent with each of the groups, {\bf WORDING NEEDS
WORK FOR CLARITY at least as close to the 10$^{\rm th}$ nearest
HDBSCAN-identified member in space-velocity coordinates as the most
peripheral HDBSCAN-identified member}.  This third step yields F, G,
and K-type stars that are spatially and kinematically close to the
photometrically-young stars, but which cannot be identified as young
based on their positions in color versus absolute magnitude.

The outcome of from the analysis up to the point of the third step is
shown in Figure~\ref{fig:XYZvtang}.  
To enable a selection cut that filters out field-star contaminants, we
also compute a weight metric, defined such that the group member
with the smallest core distance has a weight of 1, the group member
with the greatest core distance has a weight of 0, and weights for the
other group members are linearly spaced between these two extremes.
In Figure~\ref{fig:XYZvtang}, we show 26{,}960 objects with weight
exceeding 0.02 as gray points, and overplot 7{,}560 objects with
weights exceeding 0.10 as black points.

@@

Finally, there is a final step.
This paper is actually about planets, not this insane stellar
population.
We cross-matched
our candidate Cep-Her member list against 
all known Kepler Objects of Interest, including known false positives
\citep{thompson_planetary_2018}.
This yields 32 matches, of which 5 are ``confirmed''
planets according to the NASA Exoplanet Archive.
A cursory inspection of the light curves and RoboVetter (CITE)
classifications for these objects quickly revealed whether they were
consistent with being members of a $\lesssim 10^8$ year old
population.
Four candidate cluster members remained after this inspection:
Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.

Figure~\ref{fig:XYZvtang}

CH-2:
X: 20 to 80
Y: 230 to 270
Z: 70 to 105
vb: -1.5 to 3.5 kms
vl: 1 to 6 kms

RSG-5:
X: 45 to 75
Y: 320 to 350
Z: 40 to 70
vl: 4 to 6 kms
vb: -3 to -4 kms

%Querying the Gaia archive
%and imposing the cuts suggested by \citet[][Appendix
%B]{GaiaCollaboration2018} on the photometric signal to noise ratio,
%the number of visibility periods used, the astrometric $\chi^2$ of the
%single-source solution, the $G_{\rm BP}-G_{\rm RP}$ color excess
%factor and the parallax precision ($\varpi/\sigma_\varpi>5$) yields
%$\approx5.0\times10^6$ sources.
%
%Imposing a thin slice in color-absolute magnitude space around the
%pre-main-sequence of the $\delta$ Lyr cluster's previously established
%$\approx$40 Myr locus, and imposing kinematics cut for $-8 < v_b /
%{\rm km\,s^{-1}} < 0$ and $-15 < v_{l'} / {\rm km\,s^{-1}} < 15$,
%where $l'=l\cos b$, yields $\approx 5.2\times10^3$ sources.  These
%objects are all in the range BP-RP 1.5 to 3.2, so roughly K5V to
%M4.5V, or $\approx$0.2 to 0.7 solar masses.  Much more manageable, but
%according to IMF arguments, missing at least a factor of two in mass
%of any clusters.
%
%In XYZ, and in tangential velocity space, these five thousand sources
%are visually clustered in between a few to a dozen groups, depending
%on the characteristic size and velocity scales of interest.

@@

>>>>

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching the full set of candidate Cep-Her
members against known Kepler Objects of Interest (KOIs)
\citep{thompson_planetary_2018} yielded four candidate cluster
members: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.  Given our
previous analysis of Kepler-1627, we will mostly focus on the latter
three.  After analyzing the relevant properties of Cep-Her
(Section~\ref{sec:cluster}), we discuss the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of implications for the size-evolution of close-in
mini-Neptunes (Section~\ref{sec:disc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points (see Section~\ref{subsec:members}).
  Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster
  \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\} \approx
  \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$ pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  longitudinal tangential velocity versus galactic latitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.
  There is a strong spatial and kinematic overlap between Kepler-1643
  and RSG-5 ($\{ l, b\} \approx \{ 82^\circ,
  6^\circ\}$; $\{ X, Y, Z\} \approx \{60, 330, 50\} $ pc).  The
  local population of candidate young stars around KOI-7368 and
  KOI-7913 is more diffuse -- we call this region ``CH-2''.
  The {\bf interactive figure} enables a few different cuts to be
  shown.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Our focus is on a region of the Galaxy approximately 200 to 500
parsecs from the Sun, above the galactic plane, and spanning galactic
longitudes of roughly $40^\circ$ to $100^\circ$ degrees.  Two rich
clusters in this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Both of these clusters were known before Gaia, and have reported ages
between $\approx$30 and $\approx$60 million years.  Early empirical
evidence that these two clusters are likely part of a large and more
diffuse population was apparent in the Gaia-based photometric analysis
of pre-main-sequence stars by \citet[][see their Figures~11
and~13]{Zari2018}.  Further kinematic connections and complexity were
highlighted by \citet{KounkelCovey2019}, who included these previously
known groups in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{A useful visualization is available online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and tangential velocities with a subsequent manual ``stitching'' step,
and generally supports the idea that there is an overdensity of
$30$--$60\,{\rm Myr}$ old stars in this region of the Galaxy.
\citet{Kerr2021}, in a volume-limited analysis of the Gaia DR2
point-source catalog out to one third of a kiloparsec, identified
three of the nearest sub-populations, dubbed ``Cepheus-Cygnus'',
``Lyra'', and ``Cerberus''.  \citet{Kerr2021} reported ages for each
of these subgroups between 30 and 35 million years.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and a few nearby
sub-populations in this quadrant of the sky share a common origin has
yet to be fully substantiated, and will be the subject of an upcoming
study by R.~Kerr and collaborators.  Our primary interest in the
region stems from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore the
population of $10$--$100\,{\rm Myr}$ stars that were observed, we
select candidate Cep-Her members through four steps, the first three
being identical to those described in Section~3 of \citet{Kerr2021}.
We briefly summarize them here.

@@

The first step is to select stars that are photometrically distinct
from the field star population based on Gaia EDR3 magnitudes $\{G,
G_{\rm RP}, G_{\rm BP}\}$, parallaxes and auxiliary reddening
estimates \citep{lallement_gaia-2mass_2019}.  This step yielded \npms\
stars with high-quality photometric and astrometry, which are either
pre-main-sequence K and M dwarfs due to their long contraction
timescales, or massive stars near the zero-age main sequence due to
their rapid evolutionary timescales.

The second step is to then perform in an unsupervised HDBScan
clustering on the photometrically selected population
\citep{campello_hierarchical_2015,mcinnes_hdbscan_2017}.  The
parameters we use in this clustering analysis are $\{ X, Y, Z, c v_b,
c v_{l^*} \} $, where $c$ is the size-velocity corrective factor,
which is taken as $c=6\,{\rm pc / km\,s}^{-1}$ to ensure that the
spatial and velocity scales have identical standard deviations.
Positions are computed assuming the \texttt{astropy v4.0} coordinate
standard \citep{astropy_2018}, which places the Sun $8122$ pc from the
galactic center, and assumes the solar velocity with respect to the
local standard of rest from \citet{schonrich_local_2010}.  As input
parameters to HDBScan, we set the minimum $\epsilon$ threshold past
which clusters cannot be fragmented as $25$ parsecs in physical space,
and $c$ \kms\ in velocity.  The minimum cluster size $N$ is set to 10,
as is $k$, the parameter used to define the ``core distance'' density
metric.

This unsupervised clustering in our case yielded 8 distinct groups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects that are spatially and
kinematically consistent with each of the groups, {\bf IMPROVE
CLARITY at least as close to the 10$^{\rm th}$ nearest
HDBSCAN-identified member in space-velocity coordinates as the most
peripheral HDBSCAN-identified member}.  This third step yields stars
that are spatially and kinematically close to the
photometrically-young stars, but which cannot be identified as young
based on their positions in color versus absolute magnitude.

The outcome of the analysis up to the point of the third step is
shown in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that
filters out field-star contaminants, we also compute a weight metric,
defined such that the group member with the smallest core distance has
a weight of 1, the group member with the greatest core distance has a
weight of 0, and weights for the other group members are log-normally
distributed between these two extremes.  In Figure~\ref{fig:XYZvtang}, we
show 26{,}960 objects with weight exceeding 0.02 as gray points, and
overplot 7{,}560 objects with weights exceeding 0.10 as black points.
{\bf TODO: FIXME these object numbers impose pretty weak quality cuts and include junk at G>18... 
use get\_clean\_gaia\_photometric\_sources too, since they come in for
the CAMDs}.

@@

The fourth and final step was cross-matching our candidate Cep-Her
member list against all known Kepler Objects of Interest, including
known false positives \citep{thompson_planetary_2018}.  This yields 32
matches, of which 5 are ``confirmed'' planets according to the NASA
Exoplanet Archive.  A cursory inspection of the Kepler data validation
summaries and Robovetter classifications for these objects quickly
showed whether they were potentially consistent with being {\it i)}
planets, and {\it ii)} $\lesssim 10^8$ years old population, based on
the presence of rotational modulation at the expected period and
amplitude \citep[{\it e.g.},][Figure~9]{rebull_rotation_2020}.  Four
objects remained after this inspection: Kepler-1627, Kepler-1643,
KOI-7368, and KOI-7913.

Figure~\ref{fig:XYZvtang} shows the positions of the KOIs along
various projections.  Kepler-1643 is near the core RSG-5 population
both spatially and kinematically.  KOI-7368 and KOI-7913 are in a more
diffuse region $\approx$40 parsecs above RSG-5 in $Z$ and $\approx$100
parsecs closer to the Sun in $Y$.  In tangential galactic velocity
space, there may be some kinematic overlap between the region the
latter two KOIs are in, and the main RSG-5 group.

We define two sets of stars in the local vicinity of our objects of
interest, in order to verify whether they are indeed the same age.
For candidate RSG-5 members, we require:
\begin{align}
  45<X/{\rm pc}<75 \nonumber \\
  320<Y/{\rm pc}<350 \nonumber \\
  40<Z/{\rm pc}<70 \nonumber \\
  -4<v_b/{\rm km\,s^{-1}}<-3 \nonumber \\
  4<v_{l^*}/{\rm km\,s^{-1}}<6 \nonumber
\end{align}
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
	20<X/{\rm pc}<70 \nonumber \\
	230<Y/{\rm pc}<270 \nonumber \\
	75<Z/{\rm pc}<105 \nonumber \\
	-3.5<v_b/{\rm km\,s^{-1}}<-1.5 \nonumber \\
	2<v_{l^*}/{\rm km\,s^{-1}}<6, \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.
% FIXME TODO numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv right now.  Can we do better?
These cuts yield 141 candidate RSG-5 members, and 
37 candidate CH-2 members.
Given the larger volume of the latter group, and the more diffuse base
sample of stars, a major concern is contamination by field stars.
We assess this in the following section.

%Querying the Gaia archive and imposing the cuts suggested by
%\citet[][Appendix B]{GaiaCollaboration2018} on the photometric signal
%to noise ratio, the number of visibility periods used, the
%astrometric $\chi^2$ of the single-source solution, the $G_{\rm
%BP}-G_{\rm RP}$ color excess factor and the parallax precision
%($\varpi/\sigma_\varpi>5$) yields $\approx5.0\times10^6$ sources.
%
%Imposing a thin slice in color-absolute magnitude space around the
%pre-main-sequence of the $\delta$ Lyr cluster's previously
%established $\approx$40 Myr locus, and imposing kinematics cut for
%$-8 < v_b / {\rm km\,s^{-1}} < 0$ and $-15 < v_{l'} / {\rm
%km\,s^{-1}} < 15$, where $l'=l\cos b$, yields $\approx 5.2\times10^3$
%sources.  These objects are all in the range BP-RP 1.5 to 3.2, so
%roughly K5V to M4.5V, or $\approx$0.2 to 0.7 solar masses.  Much more
%manageable, but according to IMF arguments, missing at least a factor
%of two in mass of any clusters.
%
%In XYZ, and in tangential velocity space, these five thousand sources
%are visually clustered in between a few to a dozen groups, depending
%on the characteristic size and velocity scales of interest.

@@

% FIXME FIXME calculate for both!
